---
title: "Test Report"
subtitle: "An implementation in R Markdown"
author: "JJ Allaire and Yihui Xie"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
ProjectTemplate::load.project()
```

```{r define, include = FALSE}
x <- "hello" %>% paste("world", sep = ", ")
```

This is a test report. You should see the text "hello, world" in the next
sentence. `r x`.

You should also see a bar graph and a scatter plot below. (do you?)

```{r plots}
testdata %>%
  {.$x} %>%
  hist

m0.doubled %>%
  ggplot(aes(x, y)) +
  geom_point()
```

Report template stuff

# Why (purpose and motivation. Original ask)

# Summary of results (short answer to original ask)

# Detail (Actual figures and charts. Interpretation, insights etc.)

# References 
## (Any academic papers citing statistical methods or industry standards used

# Code link
